---
title: "main.py"
author: "Helene Jordan"
date: "18/7/2021"
output: html_document
---


## Libraries 

```{r, results=hide}
# devtools::install_github('charlie86/spotifyr')
library('spotifyr')
library(purrr)
library(lubridate)
library(knitr)
library(plyr)
library(ggplot2)
library(tidyr)
library(stringr)
library(dplyr)
```

## Authentication Settings

```{r}
id <- 'a498307d278a4569a85f21de1f78d5d7'
secret <- '331e4c3def7c4b7a97a0e10e1901cfa9'
Sys.setenv(SPOTIFY_CLIENT_ID = id)
Sys.setenv(SPOTIFY_CLIENT_SECRET = secret)
access_token <- get_spotify_access_token()
authorization_token <- get_spotify_authorization_code()
```

## List of users

```{r}
users <- read.csv('../../data/external/user_id.csv', header = TRUE, sep = ';')
```

## Song features

Creating an empty dataframe to store all song features

```{r}
mat = matrix(ncol = 0, nrow = 0)
  
# converting the matrix to dataframe
song_features=data.frame(mat)
all_playlists=data.frame(mat)
user_playlists=data.frame(mat)
tracks=data.frame(mat)
```

Get all playlists from users and filter the ones that were created by Spotify. 

We erase playlists created by Spotify because some spotify playlists are updated every week/every day, but that doesn't mean that the user added that playlists and those songs to their library at that time, or that he even likes the songs in there anymore. 

```{r}
for (i in users$user_url)     {
  
  # get playlists for each user
  user_playlists <- get_user_playlists(i,limit = 50)
  user_playlists$initial_user <- i
  all_playlists <- rbind(user_playlists, all_playlists)
  
  # Filter playlists created by spotify
  user_playlists <- user_playlists %>% 
    dplyr::filter(owner.display_name != 'Spotify') %>%
    dplyr::filter(name != 'Windows Media Player')
  
    for (x in user_playlists$id)   {
      tracks <- get_playlist_audio_features(playlist_uris=x)
      song_features <- rbind(song_features, tracks)
      
  }
}


```



```{r}
filtered_songs <- song_features %>%
  select(playlist_id, danceability, energy, key, loudness, mode, speechiness, acousticness, instrumentalness, liveness, valence, tempo, track.id, time_signature, added_at, track.popularity)

all_playlists <- all_playlists %>%
  select(id, tracks.total, initial_user)

all_data <- merge(x = all_playlists, y = filtered_songs, by.x = "id", by.y = "playlist_id", all.x = TRUE)
all_data <- arrange(all_data, initial_user, added_at)
all_data <- all_data %>%
  group_by(initial_user) %>%
  top_n(n = 1000, wt = added_at)
```







```{r}
user_playlists <- get_user_playlists('lauramuntaner',limit = 50)
user_playlists$initial_user <- 'lauramuntaner'
all_playlists <- rbind(all_playlists, user_playlists)
  
  # Filter playlists created by spotify
all_playlists <- all_playlists %>% 
  dplyr::filter(owner.display_name != 'Spotify')
  
    for (x in all_playlists$id)   {
      tracks <- get_playlist_audio_features(playlist_uris=x)
      song_features <- rbind(song_features, tracks)
      
  }

```

